\documentclass[nols,nofonts,notitlepage]{tufte-book}

\title{Mastering KiCad Version 5.0\thanks{Thanks to all the KiCad developers for their tireless efforts.}}
\author[Seth Hillbrand]{Seth~Hillbrand}
\publisher{}

\input{prefix.tex}

\makeindex

\begin{document}
\input{front-matter}
\cleardoublepage
\chapter*{Introduction}

\newthought{A project like KiCad} does not have a single or even primary person who is responsible for the plurality of the work.
Instead, there are many, many individuals, spread across the globe who come together over mailing lists and bug trackers to create something as a whole.
People will often drift into and out of such endeavors as their time and inclination permits.
But they leave a last, indelible and -- hopefully -- positive impact on the codebase, user experience, libraries, documentation and artwork that make up the amazing ecosystem of KiCad.

That said, a few individuals' contributions help to ensure that the ecosystem exists in the first place, that contributors are encouraged and that activity is focused where it will do the most good.
KiCad is fortunate to have (and have had) the contributions of Jean-Pierre Charras, whose work has been the foundation of KiCad and whose continued contribution to its development is an example of selfless dedication.
In addition, Dick Hollenbeck and his employer SoftPLC contributed a substantial fraction of the KiCad internals and structure.
Wayne Stambaugh who, in his role as project leader, has guided the KiCad team since 2014 and provided a much-needed steadying hand as the project developed into what it is today.
In addition to these three, there are many, many more dedicated, collaborative developers working to make KiCad stronger.

Part of making KiCad stronger is introducing it to a wider audience and, hopefully, reducing some of the headaches that accompany learning a new piece of software.
That is what I hope this book will provide.
This book is meant to supplement rather than supplant the official KiCad documentation\sidenote{\url{http://kicad-pcb.org/help/documentation/}}.
While intended aimed primarily at a University audience learning KiCad and PCB design simultaneously, I hope that it also provides a helpful reference for regular KiCad users looking to improve their usage patterns.

\mainmatter

\input{"chapter1/Introduction to KiCad.tex"}
%\input{"chapter2/KiCad Design Workflow.tex"}
%\input{"chapter3/KiCad Project Structure.tex"}
\input{"chapter4/Component Symbol Design and Library Management.tex"}
\input{"chapter5/Schematic Editor.tex"}
%\input{"chapter6/Footprint Design with KiCad.tex"}
%\input{"chapter7/Printed Circuit Board Layout.tex"}
%\input{"chapter8/Signal Integrity Design.tex"}
%\input{"chapter9/Design for Manufacturing, Design for Testing.tex"}
%\input{"chapter10/Circuit Board Tweaks and Revisioning.tex"}
\input{"chapter11/Project Design Examples.tex"}
%\input{"chapter12/SPICE Modeling in KiCad.tex"}


\backmatter

\bibliography{kicad}
\bibliographystyle{plainnat}


\printindex

\end{document}

